A Modern Take on Renormalization

### 2020-10-10 alpha/Renormalization/wilson.tex
Restructure to gather quick notes
Update note on RG

\documentclass[a4paper,10pt]{article}

\input{../preamble.tex}
\input{../modules/basics/biblatex.tex}

@@

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

\vspace*{-.5\baselineskip}
	The continuum limit $\Lambda\to\infty$ is \textbf{not} well defined.
	Renormalization provides a way to \emph{define} the theory when
	$\Lambda\to\infty$.

@@

\textbf{Key words:}
\begin{itemize}[nosep]
\item Renormalization group
\item Counterterms
\item Regularization and cutoff
\end{itemize}

@@

\noindent \textsl{Ranked by importance:}

	\begin{itemize}
	\item David Skinner's note:
	  \begin{itemize}[nosep]
	  \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT.html}
	    \begin{itemize}[nosep]
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/Wilsonchap.pdf}
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/chap5.pdf}
	    \end{itemize}
	  \end{itemize}
	\item Schwartz, Chapter 15
	\item Peskin \& Schroeder, Chapter 10 \& 12
	\item Hollowood's book:
	  \begin{itemize}[nosep]
	  \item \url{https://arxiv.org/abs/0909.0859}
	  \item \url{https://link.springer.com/book/10.1007/978-3-642-36312-2}
	  \end{itemize}
	\end{itemize}

\section{Wilson's picture}
	Seed theory parameters (i.e.\ \emph{bare parameters}):
	$(g_0,\Lambda_0)$, $g = (m,\lambda,\cdots)$ a collection of all
	possible couplings.

	\begin{equation}
	\begin{aligned}
	  \phi_{\Lambda_0}(x)
	  \sim \int^{\Lambda_0} \dd p
	    e^{ip\cdot x}
	    \tilde{\phi}(p)
	  &= \int^{\Lambda} \dd p
	    e^{ip\cdot x}
	    \tilde{\phi}(p)
	    + \int_{\Lambda}^{\Lambda_0} \dd p
	    e^{ip\cdot x}
	    \tilde{\phi}(p) \\
	  &=\colon \phi_{\Lambda}(x) + \chi(x)
	\end{aligned}
	\end{equation}

@@

	\begin{equation}
	\begin{aligned}
	  \mcal{Z} (g_0,\Lambda_0)
	  &= \int \DD \phi_{\Lambda_0}
	      e^{iS[\phi_{\Lambda_0}]} \\
	  &= \int \DD \phi_{\Lambda}
	    \int \DD \chi\,
	      e^{iS[\phi_\Lambda + \chi]} \\
	  &=\colon \int \DD \phi_{\Lambda}\,
	      e^{iS_{\mathrm{eff}} [\phi_\Lambda]}
	  =\colon \mcal{Z}\pqty{g(\Lambda),\Lambda}
	\end{aligned}
	\end{equation}
	Renormalized parameters: $(g,\Lambda)$.

	\begin{quote}
	\textbf{Subtlety:} the notation above is only schematic; in practice we
	first Wick-rotate to Euclidean signature, so that the momentum cutoff is
	easily imposed: $\norm{p} = \sqrt{p_0^2 + \vb{p}^2} < \Lambda$. In
	Lorentzian signature, it's hard to define a covariant cutoff since
	$p_\mu p^\mu = - p_0^2 + \vb{p}^2$. This process can be made rigorous;
	just think of the 8-shaped contour in loop integrals.
	\end{quote}

	\textbf{Effective action:}
	\begin{equation}
	  S_{\mathrm{eff}}[\phi]
	  = -i \ln \int \DD \chi
	      e^{iS[\phi + \chi]} \\
	\end{equation}
	$\phi = \phi_\Lambda$ is treated as constant when doing
	$\int \DD \chi$.
	\begin{equation}
	\begin{aligned}
	  \mcal{L}[\phi + \chi]
	  &= - \frac{1}{2}
	      \partial_\mu (\phi + \chi)\,
	      \partial^\mu (\phi + \chi)
	    - \frac{1}{2} m^2
	      (\phi + \chi)^2
	    - \frac{1}{4!} \lambda\,
	      (\phi + \chi)^4\\
	  &= \cdots \\
	  &= \mcal{L}[\phi]
	    + \Delta\mcal{L} [\phi,\chi]
	\end{aligned}
	\end{equation}

@@

	If $\Lambda \lesssim \Lambda_0$, then $S_{\mathrm{eff}}$ is almost
	the same as the original $S$, with minor corrections from the
	$\int \DD\chi$ term. Note that in our regularization scheme there will
	be no mixed terms of $\phi$ and $\chi$ in the effective action,
	since they have orthogonal Fourier modes.

	Note that $\mcal{Z}$ clearly does not depend on the intermediate scale $\Lambda$, we have:
	\begin{equation}
	  0
	  = \Lambda \dv{}{\Lambda}\,
	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
	  = \pqty{
	      \Lambda \pdv{}{\Lambda}
	      + \Lambda \pdv{g^{(i)}}{\Lambda}
	        \pdv{}{g^{(i)}}
	    }
	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
	\end{equation}
	This is an example of a \textbf{RG Equation}.
\section{Perturbative Renormalization}
	However, in naïve perturbation theory, we wish to complete the entire
	path integral $\mcal{Z} (g_0,\Lambda_0)$. We can think of this as
	integrating out more and more high energy modes, until we reach the IR
	scale $\Lambda \to 0$.

@@

	However, for a \emph{renormalizable} theory, we can restrict the tuning
	to a \emph{finite} dimensional subspace formed by the \emph{relevant}
	couplings, since most other parameters $g^{(i)}$ are \emph{irrelevant}
	and get suppressed by $\Lambda/\Lambda_0$ in the IR. After such
	restriction to a relevant subspace, the RG flow is a group, and we can
	reverse the flow to \emph{extrapolate} towards UV.

\subsection{Perturbation}

	The above results are non-perturbative and should always hold.
	Perturbation theory is only a way to calculate the RG flow from UV to
	IR; it is reliable only if the IR coupling $g$ is sufficiently small.
	In this case we can tune $(g_0,\Lambda_0)$ with the following
	recursive / iterative algorithm:

@@

	\hypertarget{renormalizability}{%
	\section{Renormalizability}\label{renormalizability}}

	Most parameters $g^{(i)}$ are, in fact, \emph{irrelevant} --- such
	terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR.
	If the IR theory has only \emph{relevant} couplings, then one should be
	able to recover their physical values by tuning a finite amount of
	relevant couplings in the UV, and usually the tuning is unique. This is
	the defining characteristic of a \textbf{renormalizable} theory.
	Basically, this means that we can naturally obtain a UV theory by
	extrapolation.

	\begin{quote}
	However, the tuning process described above might encounter some serious
	obstruction: the tuned $g_0$ could blow up at some finite
	$\Lambda_{\mathrm{UV}}$; this is the so-called \emph{Landau pole}.
	This tells us that the theory only works under some
	$\Lambda_{\mathrm{UV}}$, i.e.~it is not \emph{UV complete}; it's only
	an \emph{effective} theory. One have to ``embed'' this Lagrangian into a
	bigger theory that works beyond $\Lambda_{\mathrm{UV}}$; this is the
	non-trivial \emph{UV completion} of an effective theory.
	\end{quote}

@@

\section{Effective Action}

	Furthermore, after $\phi_\Lambda$ is completely integrated out, we
	have:

>>>>

\documentclass[a4paper
	,10pt
%	,twoside
]{article}

\input{../preamble.tex}
\input{../.modules/basics/biblatex.tex}

@@

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

\vspace*{-.5\baselineskip}
	\textbf{Reason:} The continuum limit $\Lambda\to\infty$ is \textbf{not} well-defined.
	Renormalization provides a way to \emph{define} the theory when
	$\Lambda\to\infty$.

@@

	\textbf{Keywords:}
	\begin{itemize}[nosep,topsep=-.5\parskip]
	\item Renormalization group
	\item Counterterms
	\item Regularization and cutoff
	\end{itemize}

@@

%\noindent \textsl{Ranked by importance:}

	\begin{itemize}[parsep=0pt,itemsep=.5\parskip]
	\item David Skinner's note:
	  \begin{itemize}[nosep]
	  \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT.html}
	    \begin{itemize}[nosep]
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/Wilsonchap.pdf}
	    \item \url{https://www.damtp.cam.ac.uk/user/dbs26/AQFT/chap5.pdf}
	    \end{itemize}
	  \end{itemize}
	\item Schwartz, Chapter 15
	\item Peskin \& Schroeder, Chapter 10 \& 12
	\item Hollowood's book:
	  \begin{itemize}[nosep]
	  \item \url{https://arxiv.org/abs/0909.0859}
	  \item \url{https://link.springer.com/book/10.1007/978-3-642-36312-2}
	  \end{itemize}
	\end{itemize}

\section{Wilson's picture}
	Seed theory parameters (i.e.\ \emph{bare parameters}):
	$(Z_\phi,g,\Lambda)_0$, where $g = (m,\lambda,\cdots)$ is the collection of all possible couplings. $Z_\phi$ is the coefficient of the kinetic term.

	\begin{equation}
	\begin{aligned}
	  \phi_{\Lambda_0}(x)
	  \sim \int^{\Lambda_0} \dd{p}
	    e^{ip\cdot x}
	    \tilde{\phi}(p)
	  &= \int^{\Lambda} \dd{p}
	    e^{ip\cdot x}
	    \tilde{\phi}(p)
	    + \int_{\Lambda}^{\Lambda_0} \dd{p}
	    e^{ip\cdot x}
	    \tilde{\phi}(p) \\
	  &=\colon \phi_{\Lambda}(x) + \chi(x)
	\end{aligned}
	\end{equation}

@@

	\begin{equation}
	\begin{aligned}
	  \mcal{Z} (g_0,\Lambda_0)
	  &= \int \DD\phi_{\Lambda_0}
	      e^{iS[\phi_{\Lambda_0}]} \\
	  &= \int \DD\phi_{\Lambda}
	    \int \DD\chi
	      e^{iS[\phi_\Lambda + \chi]} \\
	  &=: \int \DD\phi_{\Lambda}
	      e^{iS_{\mathrm{eff}} [\phi_\Lambda]}
	  =: \mcal{Z}\pqty{g(\Lambda),\Lambda}
	\end{aligned}
	\end{equation}
	Coarse-grained parameters: $(Z_\phi,g,\Lambda)$.

	\textbf{Subtlety:} the notation above is only schematic; in practice we
	first Wick-rotate to Euclidean signature, so that the momentum cutoff is
	easily imposed: $\norm{p} = \sqrt{p_0^2 + \vb{p}^2} < \Lambda$. In
	Lorentzian signature, it's hard to define a covariant cutoff since
	$p_\mu p^\mu = - p_0^2 + \vb{p}^2$. This process can be made rigorous;
	just think of the 8-shaped contour in loop integrals.

	\textbf{Effective action:}
	\begin{equation}
	  S_{\mathrm{eff}}[\phi]
	  = -i \ln \int \DD \chi
	      e^{iS[\phi + \chi]} \\
	\end{equation}
	$\phi = \phi_\Lambda$ is treated as constant when doing
	$\int \DD \chi$. Perturbatively, we integrate over loops with $\chi$ propagators as internal lines
	\begin{equation}
	\begin{aligned}
	  \mcal{L}[\phi + \chi]
	  &= - \frac{Z_\phi}{2}\,
	      \partial_\mu (\phi + \chi)\,
	      \partial^\mu (\phi + \chi)
	    - \frac{1}{2}\, m^2
	      (\phi + \chi)^2
	    - \frac{1}{4!}\, \lambda\,
	      (\phi + \chi)^4\\
	  &= \cdots \\
	  &= \mcal{L}[\phi]
	    + \Delta\mcal{L} [\phi,\chi]
	\end{aligned}
	\end{equation}

@@

	If $\Lambda \lesssim \Lambda_0$, then $S_{\mathrm{eff}}$ is almost
	the same as the original $S$, with minor corrections from the
	$\int \DD\chi$ term. Note that in such regularization scheme there will be no \textit{quadratic} cross terms $\sim \phi\chi,\, \pd\phi\,\pd\chi$ in the effective action, since they have orthogonal Fourier modes. However, there will be non-vanishing \textit{quartic} cross terms $\sim \phi^2\chi^2,\, \phi^3\chi$. After we integrate out $\chi$, the $\phi^2\chi^2$ term will cause a shift in $m^2$, while the $\phi^3\chi$ will generate a new $\phi^6$ vertex (by a $\chi\chi$ contraction).

	Note that $\mcal{Z}$ clearly does not depend on the intermediate scale $\Lambda$, and we have:
	\begin{equation}
	  0
	  = \Lambda \dv{}{\Lambda}\,
	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
	  = \pqty{
	      \Lambda \pdv{}{\Lambda}
	      + \Lambda \pdv{g^{(i)}}{\Lambda}
	        \pdv{}{g^{(i)}}
	    }\,
	    \mcal{Z}\pqty{g(\Lambda),\Lambda}
	\end{equation}
	This is an example of a \textbf{RG Equation}.
\subsection{Free theory \& CFT}
	We first observe that a massless free theory with $
		\mcal{L}[\phi]
		\sim \int \dd[d]{x} (\pd\phi)^2
	$ is ``not renormalized'' when we integrate out high energy modes. Roughly speaking, we have:
	\begin{equation}
	\begin{aligned}
	  \mcal{Z}
	  &= \int \DD\phi_{\Lambda_0}
	      e^{iS[\phi_0]} \\
	  &= \int \DD\phi_{\Lambda}
	    \int \DD\chi
	      e^{iS[\phi + \chi]} \\
	  &\sim \int \DD\phi_{\Lambda}
	      e^{iS[\phi]}
	      \sqrt{Z_\phi^\#}
	\end{aligned}
	\label{eq:PI_free}
	\end{equation}
	Integrating over $\Lambda = s\Lambda_0 \le \abs{p} \le \Lambda_0$ produces the $Z_\phi$ factor, where $\#$ is the total number of modes in this range. One can give an explicit expression of $\#$ with some IR cutoff $L$.

	On the other hand, we can restore $\Lambda = s\Lambda_0$ back to $\Lambda_0$ by rescaling. This is easy to understand when we think of a lattice theory: to probe the IR behavor, we first ``coarse-grain'' by grouping points together, effectively lowering $\Lambda$; then we ``zoom out'' to see the bigger picture. Rescaling $\Lambda = s\Lambda_0$ back to $\Lambda_0$ is precisely the ``zooming-out'' process.

	When taking $\Lambda\mapsto \Lambda_0 = \Lambda / s$, first note that the kinetic term $\int \dd[d]{x} (\pd\phi)^2$ is scale-invariant if we rescale $\phi$ accordingly:
	\begin{equation}
		\Lambda\mapsto \Lambda_0 = \Lambda / s,
	\quad
		x\mapsto x' = sx,
	\quad
		\phi(x) \mapsto
		\phi'(x') = s^{1 - \frac{d}{2}} \phi(x)
	\end{equation}
	The $s^{1 - \frac{d}{2}}$ factor is consistent with the mass dimension of $\phi$, and we have $S'[\phi'] = S[\phi]$ invariant under rescaling.

	The path integral measure, however, is \textit{not} scale-invariant; we have to add back some Fourier modes in between to return the path integral back to $\Lambda_0$. Luckily, the additional modes happen to cancels out the $Z_\phi$ factor in \eqref{eq:PI_free}:
	\begin{equation}
		\sqrt{Z_\phi^\#} \DD\phi_{\Lambda}
		\sim \sqrt{Z_\phi^\#}
			\prod_{\norm{p} < \Lambda = s\Lambda_0}
			\dd{\tilde{\phi}(p)}
		= \prod_{\norm{p'} < \Lambda_0}
			\dd{\tilde{\phi}'(p')}
		\sim \DD\phi'_{\Lambda_0}
	\end{equation}
	Therefore the complete path integral is invariant under RG flow \& rescaling; $Z_\phi$ is also unchanged during this process. Therefore we can simply set $Z_\phi \equiv 1$ by an appropriate \textit{normalization} of $\phi$.

	One can see how this process might fail in a curved background: in flat space the Fourier modes are equally spaced, and rescaling $\DD\phi_{\Lambda}$ can be achived by simply adding back a total of $\#$ modes. However, in a curved background the Fourier modes are complicated (e.g.\ think of spherical harmonics) and we generally do not expect the Jacobian of $\DD\phi_{\Lambda} \mapsto \DD\phi'_{\Lambda_0}$ to cancel out the $Z_\phi$ factor precisely. This is a hint of \textit{Weyl anomaly} in curved backgrounds. For a concrete discussion with path integral, see \textit{Di Francesco et al}, 5.A. 
\pagebreak[4]

	Generally, $Z_\phi$ \textit{will} change after rescaling:
	\begin{equation}
		Z_\phi \sim \Lambda^{-2\gamma_\phi},
	\quad
		\gamma_\phi
		\mathbin{:=}
		-\frac{1}{2}\,\Lambda \pdv{\ln Z_\phi}{\Lambda}
	\end{equation}
	The scaling of $Z_\phi$ can be absorbed by \textit{field strength renormalization} (or ``wave function'' renormalization); i.e.\ if we \textit{demand} $\phi$ to retain the canonical normalization such that $Z_\phi \equiv 1$, then $\phi$ must scale with an \textit{anomalous dimension} $\gamma_\phi$:
	\begin{equation}
		\phi(x) 
		\ \longmapsto\ %
		\phi'(x') = s^{1 - \frac{d}{2} - \gamma_\phi} \phi(x)
	\end{equation}
	In practice we don't actually redefine the scaling of $\phi$, just simplify keep track of it using the $Z_\phi$ factor; but we should know that due to quantum corrections, the mass dimension of $\phi$ is, effectively,
	\begin{equation}
		\Delta_\phi
		= \frac{d}{2} - 1 + \gamma_\phi
	\end{equation}

	In summary, we've argued that the classical \& quantum theory of a massless free boson on flat space is \textit{scale-invariant}; $\gamma_\phi = 0$. In fact, this is a first example of free CFTs. 
	CFTs are the \textit{fixed points} of RG flow.
\subsection{Massive theory \& the space of theories}
	What about \textit{massive} free theories? We do know that they don't receive loop corrections, therefore ``invariant'' under coarse-graining; however, mass \textit{do} flow when we zoom out. This is very natural; as we zoom out the energy-momentum of all modes are enhanced by a factor of $s^{-1}$, and we have $m\mapsto m/s$. Therefore $m$ is a \textit{relevant} parameter as we flow towards IR; it grows and flows away from the massless free CFT. For an explicitly path integral calculation (along with $\phi^{2n}$ interactions), see \textit{Hollowood}, 2.1.

	Generally, for small $g$ we can think of the theory $(g,\Lambda)$ as a \textit{deformation} away from the massless free CFT. A neat trick to stop worrying about rescaling is to re-define $g$ as dimensionless couplings:
	\begin{equation}
		g(\Lambda) = \pqty{
			g^{(2)} = \frac{m^2_{(\Lambda)}}{\Lambda^2},
			\ g^{(4)} = \lambda,
			\ g^{(6)} = \cdots
		}
	\end{equation}
	Here we use $m^2_{(\Lambda)}$ to denote the mass \textit{after} coarse-graining but \textit{before} rescaling. The mass term is then given by $
		\sim \int \dd[d]{x} m^2 \phi^2
		= \int \dd[d]{x} g^{(2)} \Lambda^2 \phi^2
	$. $g$ is thus invariant under rescaling, as the rescaling factor is absorbed by the $\Lambda$ factor. We also don't have to worry about the anomalous path integral measure, as it's captured by the $Z_\phi$ factor.

	After rescaling $\Lambda \mapsto \Lambda_0$, the dimensionful mass is given by:
	\begin{equation}
		m'^2_{(\Lambda)}
		= g^{(2)}_{(\Lambda)} \Lambda_0^2
		= m^2_{(\Lambda)}
			\pqty{\frac{\Lambda_0}{\Lambda}}^2
	\end{equation}
	In general, the rescaled, dimensional coupling is simply the dimensionless coupling times some factors of the \textit{initial} cutoff $\Lambda_0$. Therefore its $\Lambda$ dependence is identical to that of the dimensionless coupling. On the other hand, the coarse-grained, dimensionful couplings \textit{before} rescaling is given by $g_{\Lambda}$ times some power of $\Lambda$ (instead of $\Lambda_0$); e.g.
	\begin{equation}
		m^2_{(\Lambda)}
		= g^{(2)}_{(\Lambda)} \Lambda^2
		\xrightarrow{\ \text{free}\ }
		m_0^2
	\end{equation}
	i.e.\ it is constant for a free theory. Intuitively, this is because low \& high energy modes are completely decoupled in a free theory.

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.35\linewidth]{img/RG-flow.png}
	\end{figure}
\subsection{Physical Scales vs the Cutoff}
	LSZ reduction (with the ``mostly plus'' metric convention, see \textit{Srednicki}):
	\begin{equation}
		\int \dd[d]{x} e^{-ip\cdot x}
		\int \dd[d]{y} e^{+ik\cdot y}
		\ave[\big]{\phi(x)\,\phi(y)}
	\xmapsto{\ p,k\ \text{on-shell}\ }
		\frac{-i\sqrt{Z_\phi}}{p^2 + m^2 - i\epsilon}
		\frac{-i\sqrt{Z_\phi}}{k^2 + m^2 - i\epsilon}
		\mel{p}{S}{k}
	\end{equation}
	\begin{equation}
		\ave[\big]{\phi(x)\,\phi(y)}
		= \frac{1}{\mcal{Z}}
			\int \DD{\phi_\Lambda} e^{iS_\Lambda[\phi]}\,
			\phi(x)\,\phi(y)
	\end{equation}
	$S \sim \idty + i\mcal{M}(\mu)$, physical amplitude $\mcal{M}(\mu)$ scale with energy $\mu$, but is cutoff-independent.

	How to relate $\mcal{M}(\mu)$ to $g(\Lambda)$? Note that the canonical Green function \textit{does} scale with $\Lambda$! With the help of Poincar\'e invariance, we have:
	\begin{equation}
		Z_\Lambda \ave[\big]{\phi(x)\,\phi(y)}
		\mathbin{=:} G_\Lambda\pqty\big{x,y; g(\Lambda)}
		= G_\Lambda\pqty\big{l; g(\Lambda)},
	\quad
		Z_\lambda := (Z_\phi)_\Lambda
	\end{equation}
	Physical scale: $l = \abs{x_1 - x_2}$, or center of mass momentum $\mu$ in amplitudes; $l\cdot \mu \sim 1$. $\Lambda$-dependence enters through $Z_\phi$. For general $n$-pt function, RG flow:
	\begin{equation}
	\begin{aligned}
		\ave[\big]{\phi^n(\cdots)}
		= \frac{1}{\mcal{Z}}
			\int \DD{\phi_\Lambda} e^{iS_\Lambda[\phi]}\,
			\phi^n(\cdots)
		&= Z^{-n/2}_\Lambda
			G_\Lambda \pqty\big{l; g(\Lambda)} \\
		&= Z^{-n/2}_{s\Lambda}
			G_{\Lambda} \pqty\big{sl; g(s\Lambda)}\,
			\pqty{s^{1 - \frac{d}{2}}}^{-n}
	\end{aligned}
	\end{equation}

	This is a key result! We have:
	\begin{equation}
		G_\Lambda \pqty\big{l; g(\Lambda)}
		= G_{\Lambda} \pqty\big{sl; g(s\Lambda)}
			\pqty{
				s^{1 - \frac{d}{2}}
				\sqrt{\frac{Z_\Lambda}{Z_{s\Lambda}}}
			}^n
		\simeq G_{\Lambda} \pqty\big{sl; g(s\Lambda)}
			\,s^{n\Delta_\phi}
	\end{equation}
	Or in terms of energy scale $\mu$,
	\begin{gather}
		\mcal{M} \pqty\big{\mu; g(\Lambda)}
		= \mcal{M} \pqty\big{\mu/s; g(s\Lambda)},
	\\[1ex]
		\mu\,\pdv{\mcal{M}}{\mu}
		= \pdv{M}{g}\,\pqty{
				\Lambda\,\pdv{g}{\Lambda}
			}
	\end{gather}
\section{Perturbative Renormalization}
	However, in naïve perturbation theory, we wish to complete the entire
	path integral $\mcal{Z} (g_0,\Lambda_0)$. We can think of this as
	integrating out more and more high energy modes, until we reach the IR
	scale $\Lambda \to 0$.

@@

	However, for a \emph{renormalizable} theory, we can restrict the tuning
	to a \emph{finite} dimensional subspace formed by the \emph{relevant}
	couplings, since most other parameters $g^{(i)}$ are \emph{irrelevant}
	and get suppressed by $\Lambda/\Lambda_0$ in the IR. We shall see this in more details later. After such
	restriction to a relevant subspace, the RG flow is a group, and we can
	reverse the flow to \emph{extrapolate} towards UV.

	\begin{quote}
	\textbf{Subtlety:} the tuning process described above might encounter some serious
	obstruction: the tuned $g_0$ could blow up at some finite
	$\Lambda_{\mathrm{UV}}$; this is the so-called \emph{Landau pole}.
	This tells us that the theory only works under some
	$\Lambda_{\mathrm{UV}}$, i.e.~it is not \emph{UV complete}; it's only
	an \emph{effective} theory. One have to ``embed'' this Lagrangian into a
	bigger theory that works beyond $\Lambda_{\mathrm{UV}}$; this is the
	non-trivial \emph{UV completion} of an effective theory.
	\end{quote}

\subsection{Perturbation}
	The above results are non-perturbative and should always hold.
	Perturbation theory is only a way to calculate the RG flow from UV to
	IR; it is reliable only if the IR coupling $g$ is sufficiently small.
	In this case we can tune $(g_0,\Lambda_0)$ with the following
	recursive / iterative algorithm:

@@

\section{Renormalizability}
	As we've mentioned before, most parameters $g^{(i)} \in g$ are, in fact, \emph{irrelevant} --- such terms in the Lagrangian get suppressed by $\Lambda/\Lambda_0$ in IR. We shall see how this arise from dimensional anlaysis.

	If the IR theory has only \emph{relevant} couplings, then one should be
	able to recover their physical values by tuning a finite amount of
	relevant couplings in the UV, and usually the tuning is unique. This is
	the defining characteristic of a \textbf{renormalizable} theory.
	Basically, this means that we can naturally obtain a UV theory by
	extrapolation.

@@

\section{Effective Action}
	After $\phi_\Lambda$ is completely integrated out, we
	have:
